Polynomial phase estimation by phase unwrapping

### 2013-02-27 paper.tex
minor

In Figure~\ref{plot:m3small} the CPF estimator reaches a threshold at \unit[1]{dB}, the LSU and PHAF estimators at \unit[3]{dB} and the HAF estimator at \unit[5]{dB}.  In Figure~\ref{plot:m3small} the true coefficients are $\tilde{\mubf} = \left[ \tfrac{1}{4}, \tfrac{1}{4}, \tfrac{1}{8N}, \tfrac{1}{24N^2}  \right]$.  These are specifically chosen to satisfy the requirements of the HAF, PHAF and CPF estimators.  The HAF and PHAF estimators require that the coefficients satisfy $\tilde{\mu}_0, \tilde{\mu}_1 \in [-0.5, 0.5)$ and
\[
\tilde{\mu}_k \in \left[ -\frac{0.5}{k! \tau^{k-1}}, \frac{0.5}{k! \tau^{k-1}}\right) \qquad k = 2,3,\dots,m,
\]
where $\tau$ is the \emph{lag} and we choose $\tau = \floor{N/m}$ as suggested in~\cite{Peleg_DPT_1995,Barbarossa_PHAF_1998}.  The CPF estimator requires similar, but slightly more complicated conditions on the coefficients~\cite{Oshea_cpf_2004}.  It is informative to compare the volume of the set of coefficients suitable for the HAF, PHAF and CPF estimators with the volume of the identifiable region $B$ from~\eqref{eq:rectangular_identifiable_region}. The identifiable region has volume 
\[
\vol(B) = \prod_{k=0}^m {\frac{1}{k!}}.
\]
The volume of coefficients suitable for the HAF and PHAF estimators is
\[
\prod_{k=2}^m \frac{1}{k! \tau^{k-1}} =  \vol(B) \prod_{k=2}^m \frac{1}{\tau^{k-1}} \leq \vol(B) \prod_{k=2}^m \left( \frac{m}{N} \right)^{k-1}.
\]
The volume of the coefficients suitable for the CPF estimator can be shown to be $\tfrac{3}{2N^3} = 18 \vol(B) N^{-3}$.  It is now worth reconsidering the results in Figure~\ref{plot:m3small}.  Substituting $m=3$ and $N=199$ in the formula above, we see that the HAF and CPF estimators search a space of parameters that is almost $5 \times 10^5$ times smaller than that searched by the LSU estimator.  In this context we might expect the HAF, PHAF and CPF estimators to have thresholds at lower SNR than LSU estimator.  It is encouraging that the LSU estimator has comparable performance.  To put these results further into context, Figure~\ref{plot:m3big} repeats the simulations in Figure~\ref{plot:m3small}, but where the true coefficients are $\tilde{\mubf} = \left[ \tfrac{1}{4}, \tfrac{1}{4}, \tfrac{1}{8}, \tfrac{1}{24}  \right]$.  The CPF and HAF estimators fail spectacularly.  The performance of the LSU estimator is unchanged, as expected in view of Theorem~\ref{thm:asymp_proof}.

@@

Figure~\ref{plot:m5} displays the sample MSE of the highest order coefficient $\mu_5$  for a polynomial phase signal of order $m=5$.  In this case the LSU and PHAF estimators reach a threshold at \unit[12]{dB}, the HAF estimator at \unit[18]{dB}, and the estimator that combines the CPF and HAF at \unit[10]{dB}.  In this figure the true coefficients are $\tilde{\mubf} = \left[ \tfrac{1}{4}, \tfrac{1}{4}, \tfrac{1}{8N}, \tfrac{1}{24N^2}, \tfrac{1}{96N^3}, \tfrac{1}{480N^4}  \right]$ and these are chosen specifically to satisfy the requirement of the HAF, PHAF and CPF-HAF estimators.  As in the case where $m=3$, the region of coefficients suitable for the HAF, PHAF and CPF-HAF estimators is much smaller that the identifiable region.  The effect becomes more severe as $m$ increases.  When $m=5$ and $N=199$ the space of coefficients searched these estimators is approximately $10^{16}$ times smaller than the identifiable region.  This is a dramatic reduction in the range of detectable polynomial phase signals. Figure~\ref{plot:m5big} displays results under the same conditions as Figure~\ref{plot:m5} but with $\tilde{\mubf} = \left[ \tfrac{1}{4}, \tfrac{1}{4}, \tfrac{1}{8}, \tfrac{1}{24}, \tfrac{1}{96}, \tfrac{1}{480}  \right]$.  The conclusion is similar to that from Figure~\ref{plot:m3big}.  The performance of the LSU estimator remains unchanged, but the HAF, PHAF and CPF-HAF estimators fail completely.  The Zhou and Wang estimator can again be used to increase the range of parameters for HAF, but simulations indicate that the threshold for the estimator is approximately~\unit[103]{dB}.

>>>>

In Figure~\ref{plot:m3small} the CPF estimator reaches a threshold at \unit[1]{dB}, the LSU and PHAF estimators at \unit[3]{dB} and the HAF estimator at \unit[5]{dB}.  In Figure~\ref{plot:m3small} the true coefficients are $\tilde{\mubf} = \left[ \tfrac{1}{4}, \tfrac{1}{4}, \tfrac{1}{8N}, \tfrac{1}{24N^2}  \right]$.  These are specifically chosen to satisfy the requirements of the HAF, PHAF and CPF estimators.  The HAF and PHAF estimators require that the coefficients satisfy $\tilde{\mu}_0, \tilde{\mu}_1 \in [-0.5, 0.5)$ and
\[
\tilde{\mu}_k \in \left[ -\frac{0.5}{k! \tau^{k-1}}, \frac{0.5}{k! \tau^{k-1}}\right) \qquad k = 2,3,\dots,m,
\]
where $\tau$ is the \emph{lag} and we choose $\tau = \floor{N/m}$ as suggested in~\cite{Peleg_DPT_1995,Barbarossa_PHAF_1998}.  The CPF estimator requires similar, but slightly more complicated conditions on the coefficients~\cite{Oshea_cpf_2004}.  It is informative to compare the volume of the set of coefficients suitable for the HAF, PHAF and CPF estimators with the volume of the identifiable region $B$ from~\eqref{eq:rectangular_identifiable_region}. The identifiable region has volume 
\[
\vol(B) = \prod_{k=0}^m {\frac{1}{k!}}.
\]
The volume of coefficients suitable for the HAF and PHAF estimators is
\[
\prod_{k=2}^m \frac{1}{k! \tau^{k-1}} =  \vol(B) \prod_{k=2}^m \frac{1}{\tau^{k-1}} \leq \vol(B) \prod_{k=2}^m \left( \frac{m}{N} \right)^{k-1}.
\]
The volume of the coefficients suitable for the CPF estimator can be shown to be $\tfrac{3}{2N^3} = 18 \vol(B) N^{-3}$.  It is now worth reconsidering the results in Figure~\ref{plot:m3small}.  Substituting $m=3$ and $N=199$ in the formula above, we see that the HAF, PHAF and CPF estimators search a space of parameters that is more than $10^5$ times smaller than that searched by the LSU estimator.  In this context we might expect the HAF, PHAF and CPF estimators to have thresholds at lower SNR than LSU estimator.  It is encouraging that the LSU estimator has comparable performance.  To put these results further into context, Figure~\ref{plot:m3big} repeats the simulations in Figure~\ref{plot:m3small}, but where the true coefficients are $\tilde{\mubf} = \left[ \tfrac{1}{4}, \tfrac{1}{4}, \tfrac{1}{8}, \tfrac{1}{24}  \right]$.  The HAF, PHAF and CPF estimators fail spectacularly.  The performance of the LSU estimator is unchanged, as expected in view of Theorem~\ref{thm:asymp_proof}.

@@

Figure~\ref{plot:m5} displays the sample MSE of the highest order coefficient $\mu_5$  for a polynomial phase signal of order $m=5$.  In this case the LSU and PHAF estimators reach a threshold at \unit[12]{dB}, the HAF estimator at \unit[18]{dB}, and the estimator that combines the CPF and HAF at \unit[10]{dB}.  In this figure the true coefficients are $\tilde{\mubf} = \left[ \tfrac{1}{4}, \tfrac{1}{4}, \tfrac{1}{8N}, \tfrac{1}{24N^2}, \tfrac{1}{96N^3}, \tfrac{1}{480N^4}  \right]$ and these are chosen specifically to satisfy the requirement of the HAF, PHAF and CPF-HAF estimators.  As in the case where $m=3$, the region of coefficients suitable for the HAF, PHAF and CPF-HAF estimators is much smaller that the identifiable region.  The effect becomes more severe as $m$ increases.  When $m=5$ and $N=199$ the space of coefficients searched these estimators is approximately $10^{16}$ times smaller than the identifiable region.  This is a dramatic reduction in the range of detectable polynomial phase signals. Figure~\ref{plot:m5big} displays results under the same conditions as Figure~\ref{plot:m5} but with $\tilde{\mubf} = \left[ \tfrac{1}{4}, \tfrac{1}{4}, \tfrac{1}{8}, \tfrac{1}{24}, \tfrac{1}{96}, \tfrac{1}{480}  \right]$.  The conclusion is similar to that from Figure~\ref{plot:m3big}.  The performance of the LSU estimator remains unchanged, but the HAF, PHAF and CPF-HAF estimators fail completely.  The Zhou and Wang estimator can again be used to increase the range of parameters for the HAF, but simulations indicate that the threshold for the estimator is approximately~\unit[103]{dB}.
